\documentclass[11pt,]{article}
\usepackage[margin=1in]{geometry}
\newcommand*{\authorfont}{\fontfamily{phv}\selectfont}
  \usepackage[]{mathpazo}
  \usepackage{abstract}
\renewcommand{\abstractname}{}    % clear the title
\renewcommand{\absnamepos}{empty} % originally center
\newcommand{\blankline}{\quad\pagebreak[2]}

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}} 
\usepackage{longtable,booktabs}

\usepackage{parskip}
\usepackage{titlesec}
\titlespacing\section{0pt}{12pt plus 4pt minus 2pt}{6pt plus 2pt minus 2pt}
\titlespacing\subsection{0pt}{12pt plus 4pt minus 2pt}{6pt plus 2pt minus 2pt}

\titleformat*{\subsubsection}{\normalsize\itshape}

\usepackage{titling}
\setlength{\droptitle}{-.25cm}

%\setlength{\parindent}{0pt}
%\setlength{\parskip}{6pt plus 2pt minus 1pt}
%\setlength{\emergencystretch}{3em}  % prevent overfull lines 

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}

\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{lastpage}
\renewcommand{\headrulewidth}{0.3pt}
\renewcommand{\footrulewidth}{0.0pt} 
\lhead{}
\chead{}
\rhead{\footnotesize ERMA 7200 Basic Methods in Educational
Research -- Summer 2021}
\lfoot{}
\cfoot{\small \thepage/\pageref*{LastPage}}
\rfoot{}

\fancypagestyle{firststyle}
{
  \renewcommand{\headrulewidth}{0pt}%
  \fancyhf{}
  \fancyfoot[C]{\small \thepage/\pageref*{LastPage}}
}

%\def\labelitemi{--}
%\usepackage{enumitem}
%\setitemize[0]{leftmargin=25pt}
%\setenumerate[0]{leftmargin=25pt}




\makeatletter
\@ifpackageloaded{hyperref}{}{%
  \ifxetex
  \usepackage[setpagesize=false, % page size defined by xetex
              unicode=false, % unicode breaks when used with xetex
              xetex]{hyperref}
  \else
    \usepackage[unicode=true]{hyperref}
  \fi
}
\@ifpackageloaded{color}{
  \PassOptionsToPackage{usenames,dvipsnames}{color}
}{%
  \usepackage[usenames,dvipsnames]{color}
}
\makeatother
\hypersetup{breaklinks=true,
bookmarks=true,
pdfauthor={ ()},
pdfkeywords = {},  
pdftitle={ERMA 7200 Basic Methods in Educational Research},
colorlinks=true,
citecolor=blue,
urlcolor=blue,
linkcolor=magenta,
pdfborder={0 0 0}}
\urlstyle{same}  % don't use monospace font for urls


\setcounter{secnumdepth}{0}

\usepackage{longtable}




\usepackage{setspace}

\title{ERMA 7200 Basic Methods in Educational Research}
\author{William M. Murrah}
\date{Summer 2021}


\begin{document}  

\maketitle


\thispagestyle{firststyle}

%	\thispagestyle{empty}


\noindent \begin{tabular*}{\textwidth}{ @{\extracolsep{\fill}} lr @{\extracolsep{\fill}}}


E-mail: \texttt{\href{mailto:wmm0017@auburn.edu}{\nolinkurl{wmm0017@auburn.edu}}} & Web: \href{http://statistical-thinking.com}{\tt statistical-thinking.com}\\
Office Hours: M 2 - 4 pm, W 2 - 4 pm  &  Class Hours: Mon 4:00 pm - 8:00
pm\\
Office: 4064 Haley Center  & Class Room: Haley 2454\\
&  \\
\hline
\end{tabular*}

\vspace{2mm}



\hypertarget{course-description}{%
\section{Course Description}\label{course-description}}

The broad aim of this course is to prepare you to think like a
scientist. The goals of this course focus on preparing you to evaluate
the most common research methods used in modern educational and social
science research. This course is an introduction to the philosophical
foundations of educational research methods, and covers the major
methods of inquiry in contemporary educational research including
experimental, quasi-experimental, observational, qualitative inquiry,
and mixed-methods research. To further prepare students for current
changes in science, this course also introduces students to modern
computational research methods.

\hypertarget{course-objectives}{%
\section{Course Objectives}\label{course-objectives}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Students should become \textbf{critical consumers} of research
  reported in popular media, recognizing whether reported results
  reasonably follow from the study and analysis conducted.
\item
  Students should be able to recognize questions for which the
  \textbf{investigative process} in research would be useful and should
  be able to answer questions using the investigative process.
\item
  Students should be able to interpret \textbf{graphical displays} and
  \textbf{numerical summaries} and interpret what graphs do and do not
  reveal.
\item
  Students should demonstrate an awareness of \textbf{ethical issues}
  associated with sound statistical practice.
\item
  Students should demonstrate the ability to distinguish empirical
  research from non-empirical forms of knowledge generation.
\end{enumerate}

\newpage

\hypertarget{textbooks}{%
\section{Textbooks}\label{textbooks}}

For the first section of the course we will use the Okasha (2016) book
(see below). The rest of the course will we will use an open source
textbook and journal articles and other readings you can access online.

\hypertarget{required}{%
\subsection{Required}\label{required}}

Okasha, S. (2016). \emph{Philosophy of science: very short
introduction}. Oxford University Press.

Online textbook:

\url{https://kpu.pressbooks.pub/psychmethods4e/}

\hypertarget{graduate-teaching-assistants}{%
\section{Graduate Teaching
Assistants}\label{graduate-teaching-assistants}}

TBA

\hypertarget{course-requirements-and-evaluation}{%
\section{Course Requirements and
Evaluation}\label{course-requirements-and-evaluation}}

\emph{Learning Methods:} Lectures, demonstrations, discussions,
readings, class exercises, and other assignments.

\hypertarget{grading-policy}{%
\subsection{Grading Policy}\label{grading-policy}}

\emph{Student Assessment}

\begin{longtable}[]{@{}ll@{}}
\toprule
Assessment & percent of grade\tabularnewline
\midrule
\endhead
Homework Assignments & 25\%\tabularnewline
Quizzes & 35\%\tabularnewline
Final Project & 40\%\tabularnewline
\bottomrule
\end{longtable}

\begin{longtable}[]{@{}ll@{}}
\toprule
Grade & Scale\tabularnewline
\midrule
\endhead
A: & 90 -- 100\%\tabularnewline
B: & 80 -- 89\%\tabularnewline
C: & 70 -- 79\%\tabularnewline
D: & 60 -- 69\%\tabularnewline
F: & below 60\%\tabularnewline
&\tabularnewline
\bottomrule
\end{longtable}

\hypertarget{homework-assignments-25}{%
\subsubsection{Homework Assignments
(25\%)}\label{homework-assignments-25}}

There will be almost weekly homework assignments throughout the
semester.

\hypertarget{quizzes-35}{%
\subsubsection{Quizzes (35\%)}\label{quizzes-35}}

There will be 2 quizzes over the duration of the semester. These quizzes
will assess conceptual understanding of the topics explored in class and
reading assignments. These are to be completed without the assistance on
any resources (e.g.~no textbook, notes, or help from others). Quizzes
will be done outside of class and can be started anytime during the week
between classes, but once started students have two hours to complete.

\hypertarget{final-project-40}{%
\subsubsection{Final Project (40\%)}\label{final-project-40}}

The final project will consist of a brief annotated bibliography of 5
related peer-reviewed articles, with critiques. The The purpose of the
project is to give students the opportunity to deepen understanding of a
chosen topic. You will be asked to write a brief review of the 5
articles, focused on a key research question or questions, evaluate each
articles strengths and limitations, and demonstrates the need for
particular research. More information about the project will be provided
as the course progresses.

\hypertarget{class-policy-statements}{%
\subsection{Class Policy Statements}\label{class-policy-statements}}

\hypertarget{attendance-and-participation-policy}{%
\subsubsection{Attendance and Participation
Policy}\label{attendance-and-participation-policy}}

\begin{itemize}
\tightlist
\item
  Excellent attendance is expected. If you miss class, you will need to
  get notes from another student.
\item
  I will start class on time, so if you are late you will need to get
  notes from another student.
\end{itemize}

\hypertarget{late-assignments-policy}{%
\subsubsection{Late Assignments Policy}\label{late-assignments-policy}}

\begin{itemize}
\tightlist
\item
  Assignments turned in late will receive a 3\% reduction in earned
  points per day. The only exception will be in the case of emergency.
\item
  All work must be typed or it will not be graded. Late penalty will be
  applied to work completed in writing and then turned in late in typed
  format for a grade.
\end{itemize}

\hypertarget{honor-code-policy}{%
\subsubsection{Honor Code Policy}\label{honor-code-policy}}

\begin{itemize}
\tightlist
\item
  All portions of the Auburn University Honesty Code will apply to this
  class.

  \begin{itemize}
  \tightlist
  \item
    \href{https://sites.auburn.edu/admin/universitypolicies/Policies/AcademicHonestyCode.pdf}{Auburn
    University Honor Code}
  \end{itemize}
\item
  In addition, each student will be required to read and sign the
  following Honor Pledge when submitting class quizzes and exams.
\end{itemize}

\begin{quote}
\textbf{Honor Pledge} -- \emph{On my honor as a student, I have neither
given nor received assistance on this assignment.}
\end{quote}

\hypertarget{computer-classrooms}{%
\subsubsection{Computer Classrooms}\label{computer-classrooms}}

The Computer classrooms have a no food and drink policy. There is an
exception for bottled water, which should remain sealed when not being
consumed. If laptops are present, bottled water should be kept away from
laptops. This policy is to ensure the room remains free from liquid
stains and food crumbs that result in room repairs or the expense of
spraying for roaches. With the room being a technology room, it falls
under OIT policy and violators can lose campus computer privileges
(e-mail \& Internet access) if not adhering to this policy. If
accommodations are needed, please inform the LRC staff. Thank you for
your cooperation.

\hypertarget{incompletes-and-withdrawals}{%
\subsubsection{Incompletes and
Withdrawals}\label{incompletes-and-withdrawals}}

Grades associated with incomplete course work or withdrawal from class
will be assigned in strict conformity to University policy (see Auburn
University Bulletin). If you wish to drop this course you may do so by
the \(10^{th}\) class day with no grade assignment. From the \(10^{th}\)
class day to mid-quarter a (withdrawn-passing) grade will be recorded in
your transcripts. After this period withdrawal from the course will only
be granted under unusual circumstances and must be approved by the Dean
of the College of Education.

Note that a new incomplete grade (IN) policy is in effect. The new
policy requires that students complete a form requesting that an IN
grade be assigned. If this form in not completed and given to the
instructor of the class, a grade will be assigned with a score of zero
(0) for work that has not been completed and turned in by the time the
instructor reports grades.

\hypertarget{academic-misconduct}{%
\subsubsection{Academic Misconduct}\label{academic-misconduct}}

The Department of EFLT recognizes university policy regarding academic
misconduct. Violations include, but are not limited to: plagiarism,
unauthorized assistance during examinations, submitting another's work
product as your own, using another's words as your own without
appropriate citation, sharing unauthorized materials with another that
contain questions or answers to examinations, altering or attempting to
alter assigned grades. In accordance with University policy regarding
academic misconduct, students may be subject to several sanctions upon
violations of the Student Academic Honesty Code. See the Tiger Cub
publication for the current year for specifics regarding academic
misconduct as well as student's rights and responsibilities associated
with the Code.

\hypertarget{disability-accommodations}{%
\subsubsection{Disability
Accommodations}\label{disability-accommodations}}

Students who need special accommodations in class, as provided for by
the American Disabilities Act, should arrange a confidential meeting
with the instructor during office hours the first week of classes - or
as soon as possible if accommodations are needed immediately. You must
bring a copy of your Accommodation Memo and an Instructor Verification
Form to the meeting. If you do not have these forms but need
accommodations, make an appointment with the Program for Students with
Disabilities, 1244 Haley Center, 844-2096.

\hypertarget{academic-contingency-and-remote-instruction-modification-policy}{%
\subsubsection{Academic Contingency and Remote Instruction Modification
Policy}\label{academic-contingency-and-remote-instruction-modification-policy}}

If normal class and/or lab activities are disrupted due to illness,
emergency, or crisis situation (such another COVID outbreak), the
syllabus and other course plans and assignments may be modified to allow
completion of the course. If this occurs, an addendum to your syllabus
and/or course assignments will replace the original materials. In the
event that Auburn University institutes remote instruction for the
semester this course is offered, the following changes will be made to
the course to comply with this mandate.

Lectures, demonstrations, and other aspects of the course will be
provided as videos with screen capture and made available before the
scheduled class covering that content. In addition to other requirements
(e.g.~studying chapters from the textbook and other readings), students
will be expected to watch the videos, making notes of questions and
comments related to the material. The class will meet during the
regularly scheduled class time, but will consist of an open forum of
questions and answers related to the material. The duration of the class
time may be adjusted to reflect the replacement of lecture time with the
posted videos. Adjustments may also be made to assignments as needed.
For example, instead of in class presentations of the final project, a
written document may be required. Note that such adjustments are in
response to university mandates, and will not be made on an individual
basis.




\end{document}

\makeatletter
\def\@maketitle{%
\newpage
%  \null
%  \vskip 2em%
%  \begin{center}%
\let \footnote \thanks
{\fontsize{18}{20}\selectfont\raggedright  \setlength{\parindent}{0pt} \@title \par}%
}
%\fi
\makeatother